
# Start your response here

#### library()

library all packages I may(or may not) need.

```{r}
library(spatstat)
library(here)
library(sp)
library(rgeos)
library(maptools)
library(tmap)
library(sf)
library(geojson)
library(geojsonio)
library(tmaptools)
library(stringr)
library(tidyverse)
library(raster)
library(fpc)
library(sf)
library(dbscan)
library(ggplot2)
library(janitor)
```

## read in shp and csv data

To ensure that its coordinate reference system is correct, transform the EPSG code to New York City in shapefile. When I view the data in Excel, I find that the data set contains null values and N/A values. To avoid errors in the next phase, I set na value in the csv.

```{r}
NYdistricts <- st_read(here::here("Data_New York Evictions",
                                    "Community Districts", "geo_export_0d7e1240-f4a4-4c95-8a73-4de70e5a3c79.shp"))%>%
  st_transform(., 2263)

NYEvictions <- read_csv(here::here("Data_New York Evictions","Evictions.csv"),
                        na = c(" ","N/A"))
```

have a quick look at the district map to aviod wired area.

```{r}
qtm(NYdistricts)
```

there is nothing strange. then check the datatype of each columns in csv

```{r}
Datatypelist <- NYEvictions %>% 
  summarise_all(class) %>%
  pivot_longer(everything(), 
               names_to="All_variables", 
               values_to="Variable_class")

Datatypelist
```

## data wrangling

ignore the na values in csv,clean names and then the observations are dropped from 71,601 to 64,584

```{r}
NYEvictions <- NYEvictions %>% 
  clean_names() %>% 
  na.omit(NYEvictions)
```

### filter

filter the rows needed to match the question and keep the unique row in the data to avoid duplication, then only 2754 points are retained

```{r}
NYEvictions_fin <- NYEvictions %>% 
  dplyr::filter(str_detect(executed_date,"2020")) %>% 
  filter(residential_commercial == "Residential") %>% 
  filter(ejectment == "Not an Ejectment") %>% 
  filter(eviction_legal_possession=="Possession")

NYEvictions_fin <- NYEvictions_fin %>% 
  dplyr::distinct()
```

### transform CRS

transfer csv into sf object so that it can be mapped

```{r}
NYEvictions_fin <- NYEvictions_fin %>%
  st_as_sf(., coords = c("longitude", "latitude"), crs = 4326) %>%
  st_transform(., 2263)
```

have a quick look at the points in district map

```{r}
tmap_mode("plot")
tm_shape(NYdistricts) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(NYEvictions_fin) +
  tm_dots(col = "blue")
```

### clean the data

delete the points outside the boundary and check the map, find that no observation is removed

```{r}

NYEv_points <- NYEvictions_fin[NYdistricts,]

# check the map
tmap_mode("plot")
tm_shape(NYdistricts) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(NYEv_points) +
  tm_dots(col = "blue")
```

change the CRS into meters not feet,not sure the 32118 is correct or not

```{r}
NYdistricts <- NYdistricts %>%
  st_transform(., 32118)

NYEv_points <- NYEv_points %>%
  st_transform(., 32118)

```

## start to do the clustering analysis

### preperation

create a new window so that we can analysis them together

```{r}

window <- as.owin(NYdistricts)
plot(window)


NYEv_points <- NYEv_points %>%
  as(., 'Spatial')

NYEv_points.ppp <- ppp(x = NYEv_points@coords[,1],
                       y = NYEv_points@coords[,2],
                       window = window)

# plot it
NYEv_points.ppp %>%
  plot(.,pch=20,cex=0.5, 
       main="EVpoints in New York City")
```

### Ripley's K

why Ripley's K here is that Quadrat Analysis depends on the size of grid we set and the number of results may be very small that will influent the accuray of Quadrat Analysis. do the Ripley's K to find a suitable radius that is considered as gathering

```{r}

#K <- NYEv_points.ppp %>%
#  Kest(., correction="border") %>%
#  plot()

#Kval <- as.data.frame(Kest(NYEv_points.ppp, correction = "Ripley"))

```

it takes a long time to run the Ripleys'K on my computer and keep run to no end, so I try another way to find the eps and min points. extract the points from df and use KNN to find the eps and minpts. here k is firstly set to 15 to have a try and then try 30.

```{r}
NYEv_pointsDB <- NYEv_points %>%
  coordinates(.)%>%
  as.data.frame()

NYEv_pointsDB %>%
  dbscan::kNNdistplot(.,k=30)
```

### DBSCAN

the reason to use DBSCAN is that reply's K only shows whether there is a cluster but show nothing about where the cluster happen, that is what DBSCAN can do instead.

eps ,which is the knee of the curve, is at about 2000, and the main points is set to 30, then do the DBSCAN find that 2000km maybe too far that the whole NewYork is defined as clustering, so try smaller number of eps.finally find 800 maybe a good example.

```{r}
DB <- NYEv_pointsDB %>%
  fpc::dbscan(.,eps = 800, MinPts = 30)

plot(DB, NYEv_pointsDB, main = "DBSCAN Output", frame = F)
plot(NYdistricts$geometry, add=T)
```

The result shows that there is some cluster of Evictions in NewYork City in north and south area.

then I would like to show the output in a more clear way so I am going to do another polt.first is to input the cluster into df

```{r}
NYEv_pointsDB <- NYEv_pointsDB %>%
  mutate(dbcluster = DB$cluster)
```

create some polygons around the clustered points

```{r}
NYEv_plot <- NYEv_pointsDB %>%
  group_by(dbcluster) %>%
  dplyr::mutate(hull = 1:n(),
  hull = factor(hull, chull(coords.x1, coords.x2)))%>%
  arrange(hull)
```

delete zero because the number zero means nothing

```{r}
NYEv_plot <- NYEv_plot %>%
  filter(dbcluster >=1)
```

### make a map

when I try to use tmap to directly plot the map here, it shows error and says that "Object NYEv_plot is neither from class sf, stars, Spatial, nor Raster."So here I add a procedure to make the NYEv_plot data into sf so that can be plotted and the CRS is also set to 32118.

```{r}
NYEv_plot2 <- NYEv_plot %>%
  st_as_sf(., coords = c("coords.x1", "coords.x2"),
           crs = 32118)

```

finally use tmap to plot the map

```{r}
# find colours
colours<- get_brewer_pal("Set1", n = 10)

tmap_mode("plot")
tm_shape(NYdistricts)+
  tm_fill(col = "blue",alpha = 0.05)+
  tm_borders(lty = 2)+
tm_shape(NYEv_plot2)+
  tm_dots(col = "dbcluster",  palette = colours ,size = 0.02,style="cat")+
tm_layout(title = "New York Evictions clustering",
          title.position=c("left","top"),title.size=1)+
tm_legend(text.size =0.8,title.size=0.8) 


```



